A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
minor

\begin{figure}
	\centering
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/bfs_time.pdf}
	\end{minipage}
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/bfs_dsc.pdf}
	\end{minipage}
	\caption{The $y$-axes are logarithmic. The left box plot shows the time to compute BFS on 32 random roots while the right plot shows the times to construct the graph for each system. The Graph500 only constructs its graph once. GraphBIG reads in the file and generates the data structure simultaneously so is omitted.}
	\label{fig:bfs-time}
\end{figure}

@@

Figure~\ref{fig:bfs-scaling} shows the scalability and speedup for BFS. We define the strong scaling as $T_1 / (n T_n)$ where $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ is the time for $n$ threads. A linear scalability is when $T_n = T_1/n$ and is the horizontal line on the bottom plot in Fig.~\ref{fig:bfs-scaling}. These plots show in general poor scaling throughout, although GraphBIG has the best scaling. A potential explanation is GraphBIG is the slowest system, so there is more room for improvement. Additionally, $2^{20}$ vertices is a ``small'' graph by today's standards and thus library designers focus on scalability for larger graphs. Another limitation may be the ability for OpenMP to efficiently handle such a large number of threads per machine.
\begin{figure}
	\centering
	\begin{minipage}{0.9\linewidth}
		% trim=left lower right upper
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_speedup.pdf}
	\end{minipage}
	\begin{minipage}{0.9\linewidth}
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_ss.pdf}
	\end{minipage}
	\caption{The top figure has both axes logarithmic with an exception at 72 threads for readability. Linear speedup is. GraphMat dips below 1 because it is slower for $2$ threads than for 1. $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ time for $n$ threads.}
	\label{fig:bfs-scaling}
\end{figure}
\todo{Rerun GraphMat on scale 22 with 2 threads. Surprising that it slows down}

@@

RAPL also allows the measurement of DRAM power, the results of which are shown in Fig.~\ref{fig:power}. The left plot describes the second row of Table~\ref{tab:power} in more detail. We notice a smaller spread of RAM power consumption, but still a noticeable difference. GraphMat exhibits the lowest average RAM power consumption (but not the shortest execution time). This information can be useful when choosing an algorithm to use in limited power scenarios, where a slower algorithms that will not exceed the power cap is preferred to a faster one that may exceed it.

>>>>

\begin{figure}
	\centering
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/bfs_time.pdf}
	\end{minipage}
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/bfs_dsc.pdf}
	\end{minipage}
	\caption{The $y$-axes are logarithmic. The left box plot shows the time to compute BFS on 32 random roots while the right plot shows the times to construct the graph for each system. Graph500 only constructs its graph once. GraphBIG reads in the file and generates the data structure simultaneously so is omitted.}
	\label{fig:bfs-time}
\end{figure}

@@

Figure~\ref{fig:bfs-scaling} shows the scalability and speedup for BFS. We define the strong scaling as $T_1 / (n T_n)$ where $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ is the time for $n$ threads. A linear scalability is when $T_n = T_1/n$ and is the horizontal line on the bottom plot in Fig.~\ref{fig:bfs-scaling}. These plots show in general poor scaling throughout, although GraphBIG has the best scaling. A potential explanation is that because GraphBIG is the slowest system, there is more room for improvement. Additionally, $2^{20}$ vertices is a ``small'' graph by today's standards and thus library designers focus on scalability for larger graphs. Another limitation may be the ability for OpenMP to efficiently handle such a large number of threads per machine.
\begin{figure}
	\centering
	\begin{minipage}{0.9\linewidth}
		% trim=left lower right upper
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_speedup.pdf}
	\end{minipage}
	\begin{minipage}{0.9\linewidth}
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_ss.pdf}
	\end{minipage}
	\caption{The top figure has both axes logarithmic with an exception at 72 threads for readability. Linear speedup is. GraphMat dips below 1 because it is slower for $2$ threads than for 1. $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ time for $n$ threads.}
	\label{fig:bfs-scaling}
\end{figure}
\todo{Rerun GraphMat on scale 22 with 2 threads. Surprising that it slows down}

@@

RAPL also allows the measurement of DRAM power, the results of which are shown in Fig.~\ref{fig:power}. The left plot describes the second row of Table~\ref{tab:power} in more detail. We notice a smaller spread of RAM power consumption, but still a noticeable difference. GraphMat exhibits the lowest average RAM power consumption (but not the shortest execution time). This information can be useful when choosing an algorithm for limited power scenarios, where a slower algorithms that will not exceed the power cap is preferred to a faster one that may exceed it.
